---
title: "Trace amine-associated receptor 1 (TAAR1) agonists for psychosis - Results from the human studies <span style='font-size:25px'></style>"
author: "Spyridon Siafis, Virginia Chiocchia, Georgia Salanti <span style='font-size: 15px'></style>"
date: "`r format(Sys.Date(), '%e %b %Y')`"
output:
  html_document:
    df_print: paged
mainfont: Arialh
---

```{r setup,message=F,echo=F,include=F}
### libraries
library(meta)
library(tidyverse)
library(tibble)
library(stringr)
library(readxl)
library(grid)
library(dplyr)
library(knitr)
library(kableExtra)
library(meta)
library(devtools)
library(metafor)
library(robvis) #Need to install from devtools::install_github("mcguinlu/robvis")
library(PRISMA2020)
#devtools::install_github("haozhu233/kableExtra") I need to remove this, otherwise the R markdown didnt work


#Empty the enviroment 
rm(list=ls())

# Set option defaults
knitr::opts_chunk$set(echo = T, warning = F, message = F)

#Data cleaning routines
source("data/clean_data.R")

#Data analysis routines and functions 
source("util/analysis.R")

# Loading 
studies<-read_xlsx('data/studies_2024-01-22_LSR3_H.xlsx', na = "NA") #Descriptive data set with included studies
data <- read_xlsx('data/data_2024-01-22_LSR3_H.xlsx') #Clean data with the RCTs with available data
data_doses<-read_xlsx("data/data_doses_2024-01-22_LSR3_H.xlsx") #Effect sizes for the individual doses of TAAR1 (for a descriptive figure)
ae_categories<-read_xlsx("data/ae_categories.xlsx") #Supporting file with the names of adverse events for the summary plot for the side-effects

#prisma data
prisma<-read.csv("data/LSR3_H_PRISMA_2024.01.23.csv") #csv file for the prisma2020 
prisma<-PRISMA_data(prisma)

#risk of bias data
rob<-read_xlsx("data/rob_secondary_2024.01.24.xlsx")

#Round off results to two digits
options(scipen=1, digits=2)

```
# Description of the methodological approach

1. We analyzed usable data from all randomized controlled studies examining any TAAR1 agonist in comparison to placebo or current antipsychotics in people with psychosis, other mental health conditions, or healthy volunteers.

2. We examined efficacy outcomes, including overall symptoms of psychosis (primary) and symptom domains, dropouts due to any reason, and adverse events. Safety outcomes included death, serious adverse events, and specific adverse events. We also sought mechanistic outcomes, specifically neurobiological measures of dopaminergic, glutamatergic, and serotonergic signaling. We examined these outcomes at three time points: immediately after a single dose up to 2 weeks of treatment, 3-13 weeks of treatment (preferably at 6 weeks), and longer-term outcomes.

3. In terms of efficacy outcomes, we pooled the data for each specific subgroup, considering that differences can be expected among different diagnoses (e.g., schizophrenia and Parkinson's disease psychosis) and patient subgroups (e.g., patients with an acute episode of schizophrenia or with predominant negative symptoms). In terms of other outcomes, we combined data from all subgroups but also presented data separately for each subgroup.

4. Summary of data extraction: For continuous outcomes, we preferred change over endpoint scores and data from appropriate models or imputations considering missing outcome data. For dichotomous outcomes, we again preferred data from all participants, but in case of participants with missing outcome data, we assumed that they did not experience the event; an assumption usually used in meta-analysis in schizophrenia (e.g., Huhn et al. 2023). In terms of crossover studies, we preferred data from appropriate models considering period or carry-over effects. If not available, we assumed a correlation (i.e., 0.2 for adverse events) to correct the variance of the estimates according to Elbourne et al. 2002. If an outcome was measured multiple times after a single dose of the drug, we calculated the area under the curve according to the linear trapezoid rule (Chiou et al. 1978) and divided by the time of assessment to remove the time component.

5. Risk of bias was assessed using the RoB2 tool for parallel and crossover studies. When only one domain had some concerns, we assigned an overall low risk of bias. Otherwise, we used the worst judgment across domains.

6. The effect sizes were as follows: 1) standardized mean differences (SMD) for efficacy outcomes, given that various scales have been used in the literature to allow comparability of the findings with other studies of antipsychotic drugs; 2) mean differences (MD) for laboratory measures, i.e., weight (kg), QTc interval (msec), and prolactin levels (ng/ml); 3) odds ratios (OR) for dichotomous outcomes, which were also converted to absolute risks using a control event rate (see 7. for meta-analysis). 95% confidence intervals (95% CI) are presented, but 95% prediction intervals are not presented due to the small number of studies. Other effect sizes were not used in the first iteration of the review, e.g., those used in meta-analysis of variance due to the paucity of data.

7. Meta-analysis was conducted primarily using a random-effects model with inverse variance and REML estimator of tau-squared. Due to the small number of studies (<5) in all analyses, we corrected the confidence intervals using the Hartung-Knapp method, and we also presented the findings from fixed-effects models using the Mantel-Haenszel method throughout. Meta-analysis of proportions was conducted to pool the control groups to estimate the control event rate using logit transformation of the proportions and inverse variance method. Moreover, continuity corrections of 0.5 were applied in case of 0 events in one of the groups.

8. Sensitivity analysis of the primary outcome included using fixed-effect methods and excluding studies with an overall some concerns or high risk of bias.

9. Subgroup analyses and meta-regressions were not conducted due to the paucity of data. However, we explored potential dose-effects for the primary outcome by plotting the effect sizes for different fixed doses of TAAR1 agonists compared to placebo (while correcting for the use of common comparators).


10. Summary of evidence tables were constructed for all outcomes, including a summary of the association, biases due to study limitations, biases due to reporting bias, biases due to indirectness, and other biases. We adapted the GRADE approach. We used the ROB-ME approach for evaluating biases in missing evidence for the primary outcomes and considered the percentage of missing studies and participants for secondary outcomes. Indirectness was considered especially relevant for non-efficacy outcomes, where we pooled data across diagnoses and subgroups, and considered the percentage of studies and participants with schizophrenia, the main group for which this evidence would be applicable.

*Please see the manuscript and the protocol for more details.*

# Results

**We present below the results, including the PRISMA flow diagram, table of included studies, risk of bias assessment, and forest plots, to facilitate a better understanding of the summary of evidence tables and the manuscript. Please refer to the detailed description of the findings in the latter part of the manuscript for more information.**


## Flow of study selection

```{r echo=F, fig.fullwidth=T, fig.width=12, fig.height=8}
PRISMA_flowdiagram(prisma, previous = FALSE, other=FALSE)
```
**Figure 1** PRISMA 2020 flow diagram

## Table of included studies

```{r echo=FALSE, fig.width=12, fig.height=8}
knitr::kable(studies[, 1:14])
```

**Table 1** Table of included studies.


## Description of included studies

There were 25 eligible studies, which characteristics can be found in **Table 1**, with 20 studies (2147 participants) being completed and 5 studies being still ongoing up to 20.01.2024. There were usable data for this analysis from 9 studies (1711 participants), which enrolled adult populations across multiple countries and were funded by the industry manufactuing the TAAR1 agonists. 

The usable studies compared single or multiple doses of two TAAR1 agonists (i.e., ulotaront or ralmitaront) with placebo or current antipsychotics (i.e., risperidone or amisulpride) in people with schizophrenia, Parkinson's disease psyschosis, other mental health conditions (narcolepsy/cateplexy as sleep disorder) and healthy volunteers.
*Five studies* used a parallel design to examine the efficacy and safety of multiple doses of TAAR1 agonists in psychosis within 3-13 weeks
*Four studies* examining daily doses of TAAR1 agonists in *adults with an acute episode of schizophrenia* spectrum conditions for 4-6 weeks, 3 examined ulotaront (Koblan et al. 2020, NCT04072354 and NCT04092686) and 1 examined ralmitaront (NCT04512066). These studies used placebo as control group, and the 1 study on ralmitaront used also the antipsychotic risperidone as active comparator. *One study* comparing daily doses of ulotaront in *Parkinson's dissease psychosis* to placebo for 4 weeks (Isaacson et al. 2023).
*Four studies* examined the pharmacokinetics, safety and/or neuroimaging of single doses of TAAR1 agonists or multiple doses for up to 2 weeks: *One study* examining the effects of a single dose of 150mg ulotaront in *clinically stable adults with schizophrenia** on QTc interval within a day (Tsukada et al 2023). The study utilized a three-period crossover period comparing ulotaront with placebo and moxifloxacin (an antibiotic used as active comparator, not relevant for our analysis). *Two studies* examined the effects of single doses of ulotaront in *healthy volunteers* on sleep parameters (Hopkins et al 2021) or fMRI tasks (Perini et al 2023). Hopkins et al 2021 included two cohorts of crossover studies comparing two single doses of ulotaront with placebo. Perini et al 2023 was a parallel trial comparing ulotaront to placebo or the antipsychotic amisulpride on fMRI tasks relevant to reward, working memory and emotion processing in volunteers with high or low schizotypy traits. *One study* examined two single doses of ulotaront in *adults with narcolepsy-cateplyxy* compared to placebo using a three-period crossover design.

The following studies were unavailable:
*One study* examined the efficacy and safety of ulotaront in comparison to placebo in *adolescents with an acute episode schizophrenia* (NCT04072354). This study had two parts with adults and adolescents. This study has been recently completed, and although some usable data in the adult population are available (see above), these are not available for the adolsecents.
*One study* examined the long-term efficacy and safety of ulotaront in comparisong to the antispychotic quetiapine in *adults with clinically stable schizophrenia* (NCT04115319). The study should have been completed in 12.2022, and there are currently no usable data available.
*One study* examined monotherapy or add-on treamtent with ralmitaront in comparison to placebo in *adults with schizophrenia or schizoaffective disorder and predominant negative symptoms* (NCT03669640). The study has been recently completed in 05.2023, and it has been reported to be failed, yet no usable data were available.
*Nine studies* examined pharmacokinetics and safety of single or few multiple doses of ulotaront or ralmitaront in **healthy volunteers** (Fowler 2015, JapicCTI-194581, NCT02699372, SEP361-101, DA801002, NCT01940159, Koblan 2016, NCT04325737, NCT04865835).

The following studies are ongoing:
- *One study* is examining the efficacy and safety of two ulotaront doses of 50mg/d and 75mg/d in comparison to placebo in *adults with an acute episode of schizophrenia* (NCT04825860). The study is expected to be completed in 06.2025.
- *Two studies* are examining the efficacy and safety of ulotaront compared to placebo in other mental health conditions, i.e., adults with *major depression* (NCT05593029) and *generalized anxiety disorder* (NCT05729373). These trials are expected to be completed in 2025, and their safety data are relevant for this review.


## Risk of bias assessment

The risk of bias of the studies was examined using the RoB2 tool for parallel and crossover studies for all outcomes. Here, we present the risk of bias of using the worst judgement of a domain across outcomes. It should be noted that when there were some concerns in only one of the domains, we assigned an overall low risk of bias according to our protocol. 


```{r echo =F, fig.fullwidth=T, fig.width=7.2, fig.height=6}
rob_traffic_light(rob_all, tool="Generic")
```

**Figure 2** Risk of bias of studies with usable data

All the studies were double-blind randomized controlled studies, with a low risk of bias in most cases in their respective domains of biases due to randomization, deviations from intended interventions, and outcome measurement. There were also no indications of selectively reported results; thus, the studies had a low risk of bias in their respective domains. Most of the studies had missing outcome data, but there was no clear indication that the missingness depended on the true value of the effects for most of the outcomes. Therefore, there were some concerns, except for Isaacson et al. 2023, which had a high risk of bias for efficacy outcomes but not for adverse events and other outcomes. Additionally, there were few differences in this domain across outcomes, such as a low risk for the outcome of dropouts. In terms of the three crossover studies, there was a low risk of bias in period and carry-over effects, except for some concerns in the three-period crossover study of Tsukada et al. 2023. Few differences across outcomes can be found in the overall judgment of the risk of bias for each study per outcome in the respective forest plots below.  

## Comparison 1: *TAAR1 agonist* vs *placebo*

## Primary outcome: Overall symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks* (primary timepoint)

```{r echo=F, fig.fullwidth=T, fig.width=12, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_overall`, 
       col.diamond = "royalblue4",
       col.square =   "royalblue1",
                 rightcols = c("effect", "ci","Overall"), 
                 rightlabs = c("SMD", "95%-CI", "Risk of bias"),  
       xlim=c(-0.8,0.8),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_overall`$data$treat1_new), 
       label.c=unique(`meta_comp_taar1_vs_placebo_3-13 weeks_overall`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Placebo better", label.right="TAAR1 better")
```

**Figure 3** Forest plot for overall symptoms (primary outcome) for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Positive symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_positive`, 
       col.diamond = "royalblue4",
       col.square =   "royalblue1",
                 rightcols = c("effect", "ci", "Overall"), 
                 rightlabs = c("SMD", "95%-CI", "Risk of bias"),  xlim=c(-0.8,0.8),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_positive`$data$treat1_new),
       label.c=unique(`meta_comp_taar1_vs_placebo_3-13 weeks_positive`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Placebo better", label.right="TAAR1 better")
```

**Figure 4** Forest plot for positive symptoms for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Negative symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_negative`, 
       col.diamond = "royalblue4",
       col.square =   "royalblue1",
                 rightcols = c("effect", "ci", "Overall"), 
                 rightlabs = c("SMD", "95%-CI", "Risk of bias"),  
       xlim=c(-0.8,0.8),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_negative`$data$treat1_new), 
       label.c=unique(`meta_comp_taar1_vs_placebo_3-13 weeks_negative`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Placebo better", label.right="TAAR1 better")

```

**Figure 5** Forest plot for negative symptoms for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)


### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Depressive symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_placebo_3-13 weeks_depression`, 
       col.diamond = "royalblue4",
       col.square =   "royalblue1",
                 rightcols = c("effect", "ci", "Overall"), 
                 rightlabs = c("SMD", "95%-CI", "Risk of bias"),  xlim=c(-0.5,0.5),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_depression`$data$treat1_new),  label.c=unique(`meta_comp_taar1_vs_placebo_3-13 weeks_depression`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Placebo better", label.right="TAAR1 better")
```

**Figure 6** Forest plot for depressive symptoms for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)



### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Cognitive symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_placebo_3-13 weeks_cognition`, 
       col.diamond = "royalblue4",
       col.square =   "royalblue1",
                 rightcols = c("effect", "ci", "Overall"), 
                 rightlabs = c("SMD", "95%-CI", "Risk of bias"),  xlim=c(-0.8,0.8),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_cognition`$data$treat1_new),  label.c=unique(`meta_comp_taar1_vs_placebo_3-13 weeks_cognition`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Placebo better", label.right="TAAR1 better")
```

**Figure 7** Forest plot for cognitive impairment (measured with MMSE) for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Quality of life

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Functioning

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Response to treatment

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_response`, 
       col.diamond = "royalblue4",
       col.square =   "royalblue1",
                 rightcols = c("effect", "ci", "Overall"), 
                 rightlabs = c("OR", "95%-CI", "Risk of bias"),  xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_response`$data$treat1_new),
       label.c="placebo",
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Placebo better", label.right="TAAR1 better")

```


**Figure 8** Forest plot for response (>50% or 20% symptom reduction from baseline) for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Relapse

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Dropouts due to any reason

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_dropout_any`, 
       col.diamond = "green4",
       col.square =   "green3",
         leftcols = c("studlab",  "effect", "ci"),   
       rightcols = c("Overall"), rightlabs = c("Risk of bias"),   
                 xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_dropout_any`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")
```
**Figure 9** Forest plot for dropouts due to any reason for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks.Studies with no estimable effect size had 0 events in both arms.


### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=10, fig.height=5}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_dropout_any`, 
       col.diamond = "green4",
       col.square =   "green3",     
       label.c="placebo",
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                   xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_dropout_any`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```
**Figure 10** Forest plot for dropouts due to any reason for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)


### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Dropouts due to adverse event

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_dropout_ae`, 
       col.diamond = "green4",
       col.square =   "green3",     
       label.c="placebo",
       leftcols = c("studlab",  "effect", "ci"),      
       rightcols = c("Overall"), rightlabs = c("Risk of bias"),   
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_dropout_ae`$data$treat1_new), 
                 subgroup.hetstat = FALSE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")


```

**Figure 12** Forest plot for dropouts due to adverse event for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks. Studies with no estimable effect size had 0 events in both arms.


### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_dropout_ae`, 
       col.diamond = "green4",
       col.square =   "green3",     
       label.c="placebo",
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                   xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_dropout_ae`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")
```

**Figure 13** Forest plot for dropouts due to adverse event for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Serious adverse event

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_serious`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",          
       leftcols = c("studlab",  "effect", "ci"),   
       rightcols = c("Overall"), rightlabs = c("Risk of bias"),   
                  xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_serious`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")
```

**Figure 14** Forest plot for serious adverse events for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks. Studies with no estimable effect size had 0 events in both arms.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_serious`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",          
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                   xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_serious`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 15** Forest plot for serious adverse events for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint)


### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Death

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
#forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_death`, 
 #      col.diamond = "firebrick4",
  #     col.square =   "firebrick3",     
   #    label.c="placebo",      
    #   leftcols = c("studlab",  "effect", "ci"),           
     #  rightcols = FALSE,
      #            xlim=c(0.2,5),
       #          label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_death`$data$treat1_new), 
        #         subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
         #        overall = TRUE, prediction.subgroup = FALSE,
          #       subgroup = TRUE, fixed=TRUE, random=TRUE,
           #      label.left = "TAAR1 better", label.right="Placebo better")

```
There were available usable data from four studies (i.e., Hopkins et al 2021, Perini et al 2023, Szabo et al 2023 and Tsukada et al 2023) but all of them reported 0 deaths so that could not provide estimable effect sizes with the current approach. 

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_death`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_death`$data$treat1_new), 
                 subgroup.hetstat = FALSE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")
```

**Figure 16** Forest plot for death for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). Studies with 0 events in both arms could not provide estimable effect sizes with the current approach.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Any adverse event

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=5}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_adverse_event`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
        rightcols = c("Overall"), rightlabs = c("Risk of bias"),   
       leftcols = c("studlab",  "effect", "ci"),           
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_adverse_event`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction=FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 17** Forest plot for any adverse events for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks. 

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_adverse_event`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_adverse_event`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 18** Forest plot for any adverse event for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). 

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Anticholinergic symptoms

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_anticholinergic_symptom`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       leftcols = c("studlab",  "effect", "ci"),          
        rightcols = c("Overall"), rightlabs = c("Risk of bias"),   
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_anticholinergic_symptom`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction=FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 19** Forest plot for anticholinergic side-effects (i.e., dry mouth) for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks. 

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Hypotension

Terms that were considered as reported in the trials: hypotension or orthostatic hypotension

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_hypotension`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_hypotension`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 20** Forest plot for hypotension for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). 

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Dizziness

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_dizziness`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       leftcols = c("studlab",  "effect", "ci"),          
        rightcols = c("Overall"), rightlabs = c("Risk of bias"),   
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_dizziness`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction=FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 21** Forest plot for dizziness for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks. 

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_dizziness`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_dizziness`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 22** Forest plot for dizziness for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). 


### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Nausea or vomiting

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_nausea_vomitting`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       leftcols = c("studlab",  "effect", "ci"),          
        rightcols = c("Overall"), rightlabs = c("Risk of bias"),  
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_nausea_vomitting`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction=FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 23** Forest plot for nausea or vomiting for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks. 

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_nausea_vomitting`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_nausea_vomitting`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")


```

**Figure 24** Forest plot for nausea or vomitting for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). 

It should be noted that there appears to be some heterogeneity in the findings between ulotaront and ralmitaront. This heterogeneity may potentially be driven by the fact that ulotaront is also a 5-HT1A receptor partial agonist, which is associated with gastrointestinal symptoms. 

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: QTc prolongation

Terms that were considered as reported in the trials: QTc prolongation above ≥450 msec or an increase of ≥60 msec (any threshold was eligible)

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_qtc_prolongation`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       leftcols = c("studlab",  "effect", "ci"),          
        rightcols = c("Overall"), rightlabs = c("Risk of bias"),  
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_qtc_prolongation`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction=FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```
**Figure 25** Forest plot for QTc prolongation for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks. Studies with not estimable effect sizes had 0 events in both groups.


### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

#forest(`meta_comp_taar1_vs_placebo_3-13 weeks_qtc_prolongation`, 
 #      col.diamond = "firebrick4",
  #     col.square =   "firebrick3",     
   #    label.c="placebo",      
    #   rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
     #            label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_qtc_prolongation`$data$treat1_new), 
      #           subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
       #          overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
        #         subgroup = TRUE, fixed=TRUE, random=TRUE,
         #        label.left = "TAAR1 better", label.right="Placebo better")

```
There were available data in Koblan et al 2020, which reported 0 events in both groups, so that an effect. size cannot be estimated with the current approach. 

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: QTc interval in msec

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_qtc_interval`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       leftcols = c("studlab",  "effect", "ci"),   leftlabs = c("Study", "MD msec", "95%-CI"),       
        rightcols = c("Overall"), rightlabs = c("Risk of bias"),  
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_qtc_interval`$data$treat1_new), 
                 subgroup.hetstat = FALSE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction=FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")
```

**Figure 26** Forest plot for QTc interval in msec for the comparison of TAAR1 agonist vs. placebo at 1 day - 2 weeks. 

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Weight increased

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_weight_increased`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_weight_increased`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 27** Forest plot for weight gain for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). 


### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Weight in kg

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_weight`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("MD kg", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_weight`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")



```

**Figure 28** Forest plot for weight change in kg for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). 


### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Hyperprolactinemia

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
#forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_hyperprolactinemia`, 
 #      col.diamond = "firebrick4",
  #     col.square =   "firebrick3",     
   #    label.c="placebo",      
    #   rightcols = c("effect", "ci", "Overall"),
     #            label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_hyperprolactinemia`$data$treat1_new), 
      #           subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
       #          overall = FALSE, prediction.subgroup = FALSE, prediction=FALSE,
        #         subgroup = TRUE, fixed=TRUE, random=TRUE,
         #        label.left = "TAAR1 better", label.right="Placebo better")

```

There were available data from one study Hopkins et al 2021 reporting 0 events in both arms so that an effect size cannot be estimated with the current approach.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Prolactin levels

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_placebo_3-13 weeks_prolactin`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("MD ng/ml", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_prolactin`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```
**Figure 29** Forest plot for prolactin levels in ng/ml for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). SD was imputed from the dataset of antipsychotic trials in Huhn et al 2021.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Akathisia

Terms considered included: restlessness (when was used to describe akathisia)

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_placebo_3-13 weeks_akathisia`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_akathisia`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")


```

**Figure 30** Forest plot for akathisia for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint).


### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Extrapyramidal symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_eps_symptoms`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_eps_symptoms`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")



```
**Figure 31** Forest plot for extrapyrmidal side-effects (use of antiparkinsonian medication as proxy) for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). No data were available from the two unpublished ulotaront trials (i.e., NCT04072354, NCT04092686), the study on Parkinson disease psychosis (Isaacson 2023), and the unpublisshed study on ralmitaront (NCT04512066).

Furthermore, data presented in a conference abstract at the ACNP 2023 regarding NCT04072354 and NCT04092686 describe that ulotaront did not differ in experimental side-effect compared to placebo.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Anxiety

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

#forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_anxiety`, 
 #      col.diamond = "firebrick4",
  #     col.square =   "firebrick3",     
   #    label.c="placebo",      
    #   leftcols = c("studlab",  "effect", "ci"),   
     #            label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_anxiety`$data$treat1_new), 
      #           subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
       #          overall = FALSE, prediction.subgroup = FALSE, prediction=FALSE,
        #         subgroup = TRUE, fixed=TRUE, random=TRUE,
         #        label.left = "TAAR1 better", label.right="Placebo better")


```

There were usable data for one study Perini et al 2023, which reported 0 events in both groups so that an effect size could not be estimated with the current approach.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_anxiety`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_anxiety`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```


**Figure 32** Forest plot for anxiety for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint).



### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Agitation

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_3-13 weeks_agitation`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_agitation`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")


```


**Figure 33** Forest plot for agitation for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint).

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Headache

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_headache`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       leftcols = c("studlab",  "effect", "ci"),  
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_headache`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction=FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")
```


**Figure 34** Forest plot for headache for the comparison of TAAR1 agonist vs. placebo at 1 day to 2 weeks.


### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_placebo_3-13 weeks_headache`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_headache`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```


**Figure 35** Forest plot for headache for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint).

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Sedation

Terms that were considered as reported in the trials: fatigue, sedation, somnolence

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_placebo_1 day-2 weeks_sedation`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       leftcols = c("studlab",  "effect", "ci"),   
                 label.e = unique(`meta_comp_taar1_vs_placebo_1 day-2 weeks_sedation`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE, prediction=FALSE,
                 subgroup = TRUE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```


**Figure 36** Forest plot for sedation for the comparison of TAAR1 agonist vs. placebo at 1 day to 2 weeks.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_placebo_3-13 weeks_sedation`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_sedation`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 37** Forest plot for sedation for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint).

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Insomnia

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_placebo_3-13 weeks_insomnia`, 
       col.diamond = "firebrick4",
       col.square =   "firebrick3",     
       label.c="placebo",      
       rightcols = c("effect", "ci", "Overall"),rightlabs = c("OR", "95%-CI", "Risk of bias"),
                 label.e = unique(`meta_comp_taar1_vs_placebo_3-13 weeks_insomnia`$data$treat1_new), 
                 subgroup.hetstat = TRUE, overall.hetstat =TRUE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = TRUE, prediction.subgroup = FALSE, prediction = FALSE,
                 subgroup = FALSE, fixed=TRUE, random=TRUE,
                 label.left = "TAAR1 better", label.right="Placebo better")

```

**Figure 37** Forest plot for insomnia for the comparison of TAAR1 agonist vs. placebo at 3-13 weeks (primary timepoint). Potential differences between ulotaront and ralmitaront could be explained by their differnet pharmacological profile.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Summary plot for  dropouts and side-effects

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=8, warning=FALSE}

ae_categories<-ae_categories %>% 
  select(event_text, MedDRA_an, MedDRA_group) %>%  
  rename(outcome=MedDRA_an) 

safety_primary<-meta_outcome %>% left_join(ae_categories) %>%  #I need to change a bit 
  mutate(event_text=ifelse(outcome=="death", "Mortality", 
                           ifelse(outcome=="serious", "Serious event", 
                                  ifelse(outcome=="dropout_any", "Dropouts any reason",
                                         ifelse(outcome=="dropout_ae", "Dropouts adverse event", event_text)))),
         MedDRA_group=ifelse(outcome=="death" | outcome=="serious", "serious",
                             ifelse(outcome=="dropout_any" | outcome=="dropout_ae", "dropouts", MedDRA_group))) %>% 
  filter(!is.na(TE.random)) %>% filter(!is.na(event_text)) %>%
  mutate(point=TE.random,
         lb=TE.random-1.96*seTE.random,
         ub=TE.random+1.96*seTE.random) %>% unique() %>%
  filter(comparison=="taar1_vs_placebo")

safety_primary_timepoint<-safety_primary %>% filter(timepoint=="3-13 weeks") 


safety_primary_plot <-safety_primary %>% filter(event_text %in% safety_primary_timepoint$event_text) 

safety_primary_plot$event_text <- factor(safety_primary_plot$event_tex, levels=unique(safety_primary_plot$event_tex))
level_order<- sort(unique(safety_primary_plot$event_text))
lever_order_meddra<-c("dropouts", "any", "serious", "autonomic", "endocrinic", "neuromuscular", "neuropsychiatric")

safety_primary_plot$event_text <- factor(safety_primary_plot$event_tex, levels=unique(safety_primary_plot$event_tex))
level_order<- sort(unique(safety_primary_plot$event_text))
lever_order_meddra<-c("dropouts", "any", "serious", "autonomic", "endocrinic", "neuromuscular", "neuropsychiatric")

ggplot(data=safety_primary_plot, 
       aes(y=factor(event_text, level=rev(level_order)), x=exp(point), colour=timepoint))+
  geom_point(position=position_dodge(width = 0.5))+
  geom_errorbar(aes(x=exp(point), xmin=exp(TE.random-1.96*seTE.random), 
                    xmax=exp(TE.random+1.96*seTE.random), colour=timepoint),
                width=0, position=position_dodge(width = 0.5))+
  geom_vline(xintercept=1, linetype='dashed')+
  facet_grid(factor(MedDRA_group, levels=lever_order_meddra)~., scales = "free", space = "free")+
  scale_x_log10() +
  ylab("")+
  xlab("OR 95%CI")+
  theme_bw()


```
**Figure 38** Summary forest plot for dropouts and side-effects as dichotomous outcomes and for the two timepoints with usable data.


## Secondary outcome: Neurobiological measures relevant relevant to psychosis such as dopaminergic, glutamatergic and serotonergic signalling

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Comparison 2: *TAAR1 agonist* vs *antipsychotic*

## Primary outcome: Overall symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks* (primary timepoint)

```{r echo=F, fig.fullwidth=T, fig.width=12, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_overall`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("SMD", "95%-CI"),  
       xlim=c(-0.8,0.8),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_overall`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_overall`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Positive symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_positive`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("SMD", "95%-CI"),  
       xlim=c(-0.8,0.8),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_positive`$data$treat1_new), 
   #    label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_positive`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")
```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Negative symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_negative`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("SMD", "95%-CI"),  
       xlim=c(-0.8,0.8),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_negative`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_negative`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")
```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Depressive symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_depression`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("SMD", "95%-CI"),  
       xlim=c(-0.8,0.8),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_depression`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_depression`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Cognitive symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Quality of life

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Functioning

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Response to treatment

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_response`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
       xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_response`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_response`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")


```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Relapse

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Dropouts due to any reason

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_dropout_any`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_dropout_any`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")



```

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Dropouts due to adverse event

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_dropout_ae`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_dropout_ae`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")


```

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")


```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Serious adverse event

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_serious`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_serious`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")


```

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_serious`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_serious`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")


```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Death

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_death`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_death`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_death`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_death`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")
```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Any adverse event

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_adverse_event`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_adverse_event`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_adverse_event`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_adverse_event`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Anticholinergic symptoms

Terms that were considered as reported in the trials: dry mouth (no other relevant anticholinergic side-effects were reported such as urinary retention, constipation, mydriasis or blurred vision)

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_anticholinergic_symptom`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_anticholinergic_symptom`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Hypotension

Terms that were considered as reported in the trials: hypotension or orthostatic hypotension

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Dizziness

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_dizziness`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_dizziness`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")


```

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Nausea or vomiting

Terms that were considered as reported in the trials: nausea, vomiting, emesis

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_nausea_vomitting`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_nausea_vomitting`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_nausea_vomitting`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_nausea_vomitting`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

It should be noted that the study NCT04512066 examined ralmitaront (which compared to ulotaront is not a partial agonist of the 5-HT1A receptor)

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: QTc prolongation

Terms that were considered as reported in the trials: QTc prolongation above ≥450 msec or an increase of ≥60 msec (any threshold was eligible)

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: QTc interval in msec

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Weight increased

Terms considered included: any weight increase, weight increase >7%

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_weight_increased`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_weight_increased`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Weight in kg

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Hyperprolactinemia

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Prolactin levels

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Akathisia

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Exrapyramidal symptoms

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Anxiety

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_anxiety`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_anxiety`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}

forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_anxiety`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_anxiety`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Agitation

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_agitation`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_agitation`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")


```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Headache

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_headache`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_headache`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_headache`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_headache`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")

```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Sedation

Terms that were considered as reported in the trials: fatigue, sedation, somnolence

### Timepoint 1: *1 day - 2 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_sedation`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_1 day-2 weeks_sedation`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")
```

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Secondary outcome: Insomnia

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4}
forest(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_insomnia`, 
                 rightcols = c("effect", "ci"), 
                 rightlabs = c("OR", "95%-CI"),  
      # xlim=c(0.2,5),
                 label.e = unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_insomnia`$data$treat1_new), 
     #  label.c=unique(`meta_comp_taar1_vs_antipsychotic_3-13 weeks_dropout_any`$data$treat2_new),
                 subgroup.hetstat = TRUE, overall.hetstat =FALSE, test.subgroup.random = FALSE,test.subgroup.fixed = FALSE,
                 overall = FALSE, prediction.subgroup = FALSE,
                 subgroup = TRUE, fixed=TRUE,
                 label.left = "Antipsychotic better", label.right="TAAR1 better")
```

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Summary plot for the side-effects

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=8, warning=FALSE}
safety_primary<-meta_outcome %>% left_join(ae_categories) %>% 
  mutate(event_text=ifelse(outcome=="death", "Mortality", 
                           ifelse(outcome=="serious", "Serious event", 
                                  ifelse(outcome=="dropout_any", "Dropouts any reason",
                                         ifelse(outcome=="dropout_ae", "Dropouts adverse event", event_text)))),
         MedDRA_group=ifelse(outcome=="death" | outcome=="serious", "serious",
                             ifelse(outcome=="dropout_any" | outcome=="dropout_ae", "dropouts", MedDRA_group))) %>% 
  filter(!is.na(TE.random)) %>% filter(!is.na(event_text)) %>%  #May need to be revised a bit 
  mutate(point=TE.random,
         lb=TE.random-1.96*seTE.random,
         ub=TE.random+1.96*seTE.random) %>% unique() %>%
  filter(comparison=="taar1_vs_antipsychotic")

safety_primary_timepoint<-safety_primary %>% filter(timepoint=="3-13 weeks") 


safety_primary_plot <-safety_primary %>% filter(event_text %in% safety_primary_timepoint$event_text) 

safety_primary_plot$event_text <- factor(safety_primary_plot$event_tex, levels=unique(safety_primary_plot$event_tex))
level_order<- sort(unique(safety_primary_plot$event_text))
lever_order_meddra<-c("dropouts", "any", "serious", "autonomic", "endocrinic", "neuromuscular", "neuropsychiatric")

safety_primary_plot$event_text <- factor(safety_primary_plot$event_tex, levels=unique(safety_primary_plot$event_tex))
level_order<- sort(unique(safety_primary_plot$event_text))
lever_order_meddra<-c("dropouts", "any", "serious", "autonomic", "endocrinic", "neuromuscular", "neuropsychiatric")

ggplot(data=safety_primary_plot, 
       aes(y=factor(event_text, level=rev(level_order)), x=exp(point), colour=timepoint))+
  geom_point(position=position_dodge(width = 0.5))+
  geom_errorbar(aes(x=exp(point), xmin=exp(TE.random-1.96*seTE.random), 
                    xmax=exp(TE.random+1.96*seTE.random), colour=timepoint),
                width=0, position=position_dodge(width = 0.5))+
  geom_vline(xintercept=1, linetype='dashed')+
  facet_grid(factor(MedDRA_group, levels=lever_order_meddra)~., scales = "free", space = "free")+
  scale_x_log10() +
  ylab("")+
  xlab("OR 95%CI")+
  theme_bw()


```

## Secondary outcome: Neurobiological measures relevant relevant to psychosis such as dopaminergic, glutamatergic and serotonergic signalling

### Timepoint 1: *1 day - 2 weeks*

No usable data available from RCT.

### Timepoint 2: *3 weeks - 13 weeks*

No usable data available from RCT.

### Timepoint 3: *\> 13 weeks*

No usable data available from RCT.

## Subgroup analyses and meta-regressions

We did not conduct subgroup analyses and meta-regressions for the primary outcome due to the small number of included studies (i.e., 5) that precluded the exploration of potential reasons of heterogeneity.

### Descriptive exploration of potential dose-effects

We wanted to further explore the potential dose-effects of ulotaront or ralmitaront on improving overall symptoms in acute patients with schizophrenia, given that their doses were pooled in the analyses mentioned above. For this reason, we caclulated the effect sizes of each of the doses of these drugs compared to placebo (correcting the smaple of placebo as a shared control in a trial), and we plotted them in the figure below. *No clear dose-effects can be observed.*

```{r echo=F, fig.fullwidth=T, fig.width=11, fig.height=4, warning=FALSE}
ggplot(data=data_doses, aes(x=dose,
                                 y=-yi,
                                 ymin=-yi+1.96*sqrt(vi), ymax=-yi-1.96*sqrt(vi), 
                                 group=study_name, colour=study_name))+
  geom_pointrange(position=position_dodge(width = 1.2), aes(shape=schedule), size=1)+
  xlim(c(0,150))+
  coord_cartesian(ylim=c(-0.5,0.5), expand=TRUE)+
  xlab("dose (mg//d)")+
  ylab("SMD 95%CI")+
  scale_shape_manual(values = c(15,0), guide=FALSE)+
  geom_hline(yintercept = 0, linetype="dashed")+
  facet_wrap(~drug_name,  scales = "free", nrow=2)+
  theme_bw()
```

\*It should be noted that Koblan 2020 was a two-arm flexible dose study, and its effect size is placed in the middle of the range of the administered dose (50mg/d to 75mg/d), yet the median or mean dose in the trial could be different and was not reported. \*\*The study of Isaacson 2023 was not presented here, as it was included participants with Parkinson disease psychosis.


We further conducted a dose response meta-analysis by standardizing the dose between ulotaront and ralmitaront by taking into consdieration their E50 (see HTML animal studies --- text to be revised --- probably this analysis will be deeted)
```{r echo=F, fig.fullwidth=T, fig.width=5, fig.height=3, warning=FALSE}
ggplot(data= pred, aes(x= dose, y = pred))+
  xlab("Standardized Dose")+
  ylab("SMD 95%")+
  geom_line(size=1)+
  geom_rug(data=master_dose, mapping=aes(x=standardized_dose, y= 0)) +
  geom_line(data=pred, aes(x= dose, y = ci.lb), linetype='dashed', size=0.7)+
  geom_line(data=pred, aes(x= dose, y = ci.ub), linetype='dashed',size=0.7)+
  geom_hline(yintercept = 0, colour='black', size=0.2)+
  theme_bw()
```



## Sensitivity analyses

We did not conduct the following pre-planned sensitivity analyses for the primary outcome due to the small number of included studies (i.e., 5), i.e., 1) restricting the analysis to studies with an overall low risk of bias (no study had an overall low risk of bias) and 2) excluding estimates with imputed values (the N and SD of the ulotaront unpublished studies was imputed.

## Reporting bias

We evaluated the potential reporting bias for the primary outcome (overall symptoms in acute psychosis) using the ROB-ME tool.

### Results matrix for the primary outcome

```{r echo=FALSE}
studies_primary<-studies %>% filter(Name=="NCT04512066 (2020)"  | Name=="Isaacson (2023)" | Name=="NCT04072354 (2019)" |
                                      Name=="Koblan (2020)" |Name== "NCT04092686 (2019)" | Name== "NCT04825860 (2021)") %>%  mutate(Diagnosis=ifelse(Name=="Isaacson (2023)", "Parksinon disease psychosis", "Schizophrenia spectrum"), `Data availability`=ifelse(Name== "NCT04825860 (2021)", "~", 
                                                                                                                                                                                                                                                                   ifelse(Name=="NCT04072354 (2019)","✓ (adult) / ?(adolescent) " , "✓"))) %>%
  select(Name, Diagnosis, `Sample size`, `Data availability`) 

knitr::kable(studies_primary[order(studies_primary$Diagnosis, studies_primary$Name),])
```

✓: A study result is available for inclusion in the meta-analysis.; \~:No study result is available for inclusion in the meta-analysis, for a reason unrelated to the P value, magnitude or direction of the result.; ?: Unclear whether an eligible study result was generated. \*NCT04072354 included two parts, i.e., adults (sample size 435) and adolescents (sample size unclear but probably 28; planned 90). It should be noted that all of the other studies included adult populations. \*\*NCT04825860 is an ongoing trial.

### Funnel plots and examination of small-study effects

There were no sufficient data (i.e., 5 studies \< 10) to examine small-study effects with funnel plots.

### Coverage of the search strategy

We conducted a comprehensive search of published and unpublished studies. Although we have not contacted the pharmaceutical companies (Hoffman-Roche for ralmitaront, and Sunovion/Sumitomo for ulotaront), it is not expected that any study was not identified in the search, as all of the trials were very recently published, and they should all have been registered.

### ROB-ME evaluation

There were no missing results in the studies identified (except for one small trial in adolescnets which data should not have an impact on the findings).There wre also no circumstances indicating potential for missing studies, and no clear patter of the results indicate potential missing studies (although funnel plots could not have been conducted due to the small number of studies). The same evaluation is relevant for both the comparisons of TAAR1 agonists vs. placebo and TAAR1 agonsits vs. antipsychotics. Therefore, there was assigned a low risk of bias in reporting bias.

## Summary of the evidence on the primary outcome from the human studies

### Summary of the evidence tables

The primary outcome was efficacy in reducing overall symptoms in acutely ill patients with psychosis, i.e., available data for adults with Parkinson disease psychosis and schizophrenia spectrum (analyzed separately). There were available data for two comparisons, i.e., TAAR1 agonists (ulotaront or ralmitaront) vs. placebo, and TAAR1 agonist (ralmitaront) vs. antipsychotics (risperidone). The summary of the evidence on the primary outcome for the above mentioned populations and comparisons are reported below.

|                                                                                       |                                                       |                                                                                                                                                             |                                |                                                                                                                                                                                               |                                                                                                                                                                                             |
|------------|------------|------------|------------|------------|------------|
| **Source of evidence**                                                                | **Summary of the association**                        | **Bias due to study limitations**                                                                                                                           | **Bias due to reporting bias** | **Bias due to indirectedness**                                                                                                                                                                | **Bias due to other reasons**                                                                                                                                                               |
| TAAR1 agonist. vs placebo in adults with Parkinson disease psychosis                  | n=1, k=37, SMD= -0.28, 95%CI: -0.95, 0.38             | 100% of the studies had an overall high risk of bias (due to missing outcome data, unclear direction and impact on the findings)                            | Low risk of reporting bias     | Data available only for ulotaront. No other clear indication of indirectness in terms of population, interventions and outcomes                                                               | No clear indication of other biases                                                                                                                                                         |
| TAAR1 agonist. vs placebo in adults with schizophrenia spectrum disorder              | n=4, k=1291, SMD=0.15, 95%CI: -0.05, 0.34, tau2=0.024 | All studies had an overall low risk of bias (some concerns due to missing outcome data, unclear direction and impact on the findings - potentially minimal) | Low risk of reporting bias     | Data available only for ulotaront (3 studies) and ralmitaront (1 study).No other clear indication of indirectness in terms of population, interventions and outcomes                          | The phase III ulotaront trials conducted during COVID-19, which could be associated with factors assocaited with increased placebo effects and smaller effect sizes. No clear dose-effects. |
| TAAR1 agonist. vs other antipsychotics in adults with schizophrenia spectrum disorder | n=1, k=156, SMD=-0.53, 95%CI: -0.86, -0.20            | One study with an overall low risk of bias (some concerns due to missing outcome data, unclear direction and impact on the findings - potentially minimal)  | Low risk of reporting bias     | Data available only for ralmitaront (no data for ulotaront) and risperidone (no data for other antipsychotics). No other clear indication of indirectness in terms of population and outcomes | No clear indication of other biases                                                                                                                                                         |

k: number of studies, n: number of participants, I2: I-squared, SMD\>0 indicates a favourable effect for the TAAR1 agonist. It should be noted that there is low confidence evidence that studies with high risk of bias in misisng outocme data may underestimate the effects (PMID: 37939743).

### GRADE approach in evaluating the confidence in the evidence

#### What are the effects of TAAR1 agonists versus placebo on overall symptoms in adults with acute schizophrenia spectrm disorder?

TAAR1 agonists may have little to no effect compared to placebo on overall symptoms in acutely ill adults with schizophrenia spectrum disorder (SMD=0.15, 95%CI: -0.05, 0.34). Specifically, the confidence in the evidence was *low* due to some concerns in imprecision (95%CI crossed line of no differences and 0.1) and some concerns in heterogeneity (although could not be well estimated due to the small number of studies).

#### What are the effects of TAAR1 agonists versus antipsychotics on overall symptoms in adults with acute schizophrenia spectrm disorder?

TAAR1 agonists may be less efficacious with a medium effect size compared to other antipsychotics in improving overall symptoms in acutely ill adults with schizophrenia spectrum disorder (SMD=-0.53, 95%CI: -0.86, -0.20). The confidence in the evidence was *low* due to some concerns in imprecision (although 95%CI did not cross the range of equivalence, the sample size was small \<800 participants) and some concerns in indirectness (no data ulotaront and other antipsychotics).

#### What are the effects of TAAR1 agonists versus placebo on overall symptoms in adults with Parkinson disease psychosis?

TAAR1 agonists may have little to no effect compared to placebo on overall symptoms in acutely ill adults with Parkinson disease psychosis (SMD=-0.28, 95%CI: -0.95, 0.38) and the evidence is very uncertain. Specifically, the confidence in the evidence was *very low* due to major concerns in imprecision (95%CI crossed beyond SMD -0.1 and 0.1, and the sample size was very small \<800 participants), and some concerns in the risk of bias (study with a high risk of bias).

## Summary of the evidence tables for all outcomes

```{r echo=FALSE}
knitr::kable(meta_outcome_soe[, 1:8])
```

